Supporting Information

### 2018-03-17 SupportingInformation.Rmd
adding ext risk for LC model

```{r fn_varying_d, echo=F}
varying_d<-function(numsims,numsteps,numlocs,r,K){
  risk_right<-c()
  risk_left<-c()
  d_seq<-seq(from=0,to=1,by=0.01)
  for(d in d_seq){
    riskrl<- plotter_ext_risk(numsims=numsims,numsteps = numsteps,numlocs = numlocs,d=d,r=r,K=K,ploton=F)
    risk_r<-riskrl$risk_right_after_numsteps
    risk_l<-riskrl$risk_left_after_numsteps
    risk_right<-c(risk_right,risk_r)
    risk_left<-c(risk_left,risk_l)
  }
  par(mfrow=c(1,2))
  plot(d_seq,risk_right,xlab='d',ylab='Risk_right',ylim=c(0,max(risk_right)),type="b",col="blue",panel.first = grid())
  plot(d_seq,risk_left,xlab='d',ylab='Risk_left',ylim=c(0,max(risk_left)),type="b",col="red",panel.first = grid())
  #mtext("red : left tail-dep, blue : right tail-dep")
}
```

```{r fig_risk_K50, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=50, numlocs=10, numsteps=25, numsims=1000.\\label{fig_risk_K50}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=10,r=1,K=50)
```

```{r fig_risk_K100, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=100, numlocs=10, numsteps=25, numsims=1000.\\label{fig_risk_K100}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=10,r=1,K=100)
```

```{r fig_risk_K200, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=200, numlocs=10, numsteps=25, numsims=1000.\\label{fig_risk_K200}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=10,r=1,K=200)
```

```{r fig_risk_numlocs5, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=100, numlocs=5, numsteps=25, numsims=1000.\\label{fig_risk_numlocs5}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=5,r=1,K=100)
```

```{r fig_risk_numlocs15, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=100, numlocs=15, numsteps=25, numsims=1000.\\label{fig_risk_numlocs15}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=10,r=1,K=100)
```

```{r fig_risk_numlocs25, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=100, numlocs=25, numsteps=25, numsims=1000.\\label{fig_risk_numlocs25}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=15,r=1,K=100)
```

  * With increasing $K$, extinction risk decreases [for a fixed $d$ , $r$ and $numlocs$] but this effect is more prominent in
case of left tail-dep data. [see Figure \ref{fig_risk_K50} - Figure \ref{fig_risk_K200}]

  * With increasing $numlocs$, extinction risk decreases [for a fixed $d$ , $r$ and $K$] but this effect is more prominent in
case of left tail-dep data. [see Figure \ref{fig_risk_numlocs5} - Figure \ref{fig_risk_numlocs25}]

>>>>

```{r fn_varying_d, echo=F}
varying_d<-function(numsims,numsteps,numlocs,r,K){
  risk_right<-c()
  risk_left<-c()
  d_seq<-seq(from=0,to=1,by=0.01)
  for(d in d_seq){
    riskrl<- plotter_ext_risk(numsims=numsims,numsteps = numsteps,numlocs = numlocs,d=d,r=r,K=K,ploton=F)
    risk_r<-riskrl$risk_right_after_numsteps
    risk_l<-riskrl$risk_left_after_numsteps
    risk_right<-c(risk_right,risk_r)
    risk_left<-c(risk_left,risk_l)
  }
  par(mfrow=c(1,2))
  plot(d_seq,risk_left,xlab='d',ylab='Risk_left',ylim=c(0,max(risk_left)),type="b",col="red",panel.first = grid())
  plot(d_seq,risk_right,xlab='d',ylab='Risk_right',ylim=c(0,max(risk_right)),type="b",col="blue",panel.first = grid())
  #mtext("red : left tail-dep, blue : right tail-dep")
}
```

### LC model :
```{r fig_risk_r0_numlocs5, echo=F, fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal) for numlocs=5, numsteps=25, numsims=1000.\\label{fig_risk_r0_numlocs5}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=5,r=0,K=50)
```

```{r fig_risk_r0_numlocs25, echo=F, fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal) for numlocs=25, numsteps=25, numsims=1000.\\label{fig_risk_r0_numlocs25}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=25,r=0,K=50)
```

  *  As expected, when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one. With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] but this effect was more prominent in case of data came from right tail-dep environmental noise. [see Figure \ref{fig_risk_r0_numlocs5} - Figure \ref{fig_risk_r0_numlocs25}].

### Ricker model :

```{r fig_risk_r1_K100, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=100, numlocs=10, numsteps=25, numsims=1000.\\label{fig_risk_r1_K100}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=10,r=1,K=100)
```

```{r fig_risk_r1_K200, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=200, numlocs=10, numsteps=25, numsims=1000.\\label{fig_risk_r1_K200}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=10,r=1,K=200)
```

```{r fig_risk_r1_numlocs5, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=100, numlocs=5, numsteps=25, numsims=1000.\\label{fig_risk_r1_numlocs5}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=5,r=1,K=100)
```

```{r fig_risk_numlocs25, echo=F, fig.cap="Plot Extinction risk vs. d(degree of dispersal) for r=1, K=100, numlocs=25, numsteps=25, numsims=1000.\\label{fig_risk_r1_numlocs25}", fig.height=4, fig.width=8}
varying_d(numsims=1000,numsteps =25,numlocs=25,r=1,K=100)
```

  * With increasing $K$, extinction risk decreases [for a fixed $d$ , $r$ and $numlocs$] but this effect is more prominent in
case of left tail-dep data. [see Figure \ref{fig_risk_r1_K100} - Figure \ref{fig_risk_r1_K200}]

  * With increasing $numlocs$, extinction risk decreases [for a fixed $d$ , $r$ and $K$] but this effect is more prominent in
case of left tail-dep data. [see Figure \ref{fig_risk_r1_numlocs5} - Figure \ref{fig_risk_r1_numlocs25}]
